Sea-ice and macrozooplankton distribution as determinants of top predator community structure in Antarctic winter

### 2024-06-13 analysis/paper/paper.qmd
table s2

Predator densities varied among clusters (Table S2). Snow petrels and Adélie penguins had the greatest overall density across clusters (1.665 and 1.153 ind. km^–1^, respectively), though their densities were greatest in the marginal ice zone (3.116 and 4.036 ind. km^–1^, respectively). Other abundant predators in the marginal ice zone included Antarctic fur seals (2.892 ind. km^–1^), crabeater seals (0.437 ind. km^–1^), Antarctic petrels (0.258 ind. km^–1^), and kelp gulls (0.158 ind. km^–1^). Antarctic fur seals and snow petrels were ubiquitous in the marginal ice cluster (observed at 100.0 and 96.3% of sites, respectively). Despite their high densities, Adélie penguins were only observed at 42.6% of sites in the marginal ice cluster (compared to 67.9% of pack ice sites).

@@

>>>>

Predator densities varied among clusters ([@supptbl-densfreq]). Snow petrels and Adélie penguins had the greatest overall density across clusters (1.665 and 1.153 ind. km^–1^, respectively), though their densities were greatest in the marginal ice zone (3.116 and 4.036 ind. km^–1^, respectively). Other abundant predators in the marginal ice zone included Antarctic fur seals (2.892 ind. km^–1^), crabeater seals (0.437 ind. km^–1^), Antarctic petrels (0.258 ind. km^–1^), and kelp gulls (0.158 ind. km^–1^). Antarctic fur seals and snow petrels were ubiquitous in the marginal ice cluster (observed at 100.0 and 96.3% of sites, respectively). Despite their high densities, Adélie penguins were only observed at 42.6% of sites in the marginal ice cluster (compared to 67.9% of pack ice sites).

@@

::: {#supptbl-densfreq}
```{r}
make_tbl_densfreq(read_obj("predators_clust"), 
                  read_obj("stations_clust"), 
                  read_obj("station_effort"))

Density (ind km^-1^) and frequency (% sites present) of predators within and across clusters. See @tbl-predators for scientific names. Note: we removed sites with no observed predators from the cluster analysis, so the frequencies in the **All clusters** column are greater than the frequencies in @tbl-predators (which included sites without predators).
:::
